---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  dpi = 300,
  message = FALSE
)
```

# R code for GLR paper

<!-- badges: start -->
<!-- badges: end -->

This repository contains R scripts reproducing all figures and analyses presented in the paper *Kinship cases with partially specified hypotheses* (Egeland & Vigeland, FSI:Genetics, 2025, https://doi.org/10.1016/j.fsigen.2025.103270).

For example, the following code creates and plots the pedigrees of the *Motivational example*, where the aim is to test if individual A is the grandmother of individual B:

```{r fig.width = 6, fig.height = 2.5, out.width = "80%"}
library(pedtools)

# Undisputed pedigree part
ped = linearPed(2) |> relabel(c("GF", "A", "FA", "MO1", "C"))

# Three possible pedigrees
peds = list(
  Ped1 = ped |> addDaughter(c("FA", "MO1"), id = "B") |> reorderPed(c("B", "C")),
  Ped2 = ped |> addDaughter(c("FA", "MO2"), id = "B") |> reorderPed(c("B", "C")),
  Ped3 = list(ped, singleton("B", sex = 2))
)

# Quick glance: 
# plotPedList(peds)

# Plot
plotPedList(peds, hatched = c("A", "B", "C"), 
            labs = c("A", "B", "C"),
            groups = list(1:2, 3:4), 
            titles = c("H1: A grandmother of B", "H2: A and B unrelated"), 
            grouptitlesArgs = list(line = 1.1, cex = 0.9, font = 1))
```

Complete code (reproducing the stylised published version)
can be found in the folder `example1-grandmother` of this repository. 


